### 2015-09-10 vmcai-2016-tex/approach.tex
Corrected numerous typos throughout the paper.

We visualize the initialization process in~\figref{fig:initHeap}. The
graph in~\figref{fig:initHeap}(a) represents the initial heap. The
reference superscripts $s$ and $i$ indicate the partition containing
the reference.  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a
stack reference for the $\cfgt{this}$ variable which has two fields
$x$ and $y$ of the same type. Note that when no constraint is
specified for a location, there is an implicit $\mathit{true}$
constraint. For example, $\cfgnt{r}_0^s$ points to $\cfgnt{l}_0$ on
the constraint $\mathit{true}$. The fields $x$ and $y$ point to the
uninitialized reference $\cfgnt{r}_\mathit{un}$. The graph
in~\figref{fig:initHeap}(b) represents the symbolic heap after the
initialization of the $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$ field
while the graph in~\figref{fig:initHeap}(c) represents the symbolic
heap after the initialization of the
$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$ field following the
initialization of $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$. The list
in~\figref{fig:initHeap}(d) represents the various sets constructed in
initialization rule for $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$. We
also define values of constraints used as labels in the graph.

@@

There are two rewrite rules in~\figref{fig:fHeap}(a), one for reading
the value of a field (field-access) and the other when we write to a
field (field-write). Both rules first check that the operations can be
performed on a non-null location. The field-access rewrite rule
in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$ and
uses \figref{fig:symInit}, to get a new symbolic heap that is
initialized on the field $\cfgnt{f}$. The symbolic heap is further
modified to include a new stack reference pointing to the value set
(possible values of the field) returned during the dereferencing; the
new stack reference is the return value from the operation.

>>>>

We visualize the initialization process in~\figref{fig:initHeap}. The
graph in~\figref{fig:initHeap}(a) represents the initial heap. The
reference superscripts $s$ and $i$ indicate the partition containing
the reference.  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a
stack reference for the $\cfgt{this}$ variable which has two fields
$x$ and $y$ of the same type. Note that when no constraint is
specified for a location, there is an implicit $\mathit{true}$
constraint. For example, $\cfgnt{r}_0^s$ points to $\cfgnt{l}_0$ on
the constraint $\mathit{true}$. The fields $x$ and $y$ point to the
uninitialized reference $\cfgnt{r}_\mathit{un}$. The graph
in~\figref{fig:initHeap}(b) represents the symbolic heap after the
initialization of the $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$ field
while the graph in~\figref{fig:initHeap}(c) represents the symbolic
heap after the initialization of the
$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$ field following the
initialization of $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$. The list
in~\figref{fig:initHeap}(d) represents the various sets constructed in
the initialization $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$.

@@

There are two rewrite rules in~\figref{fig:fHeap}(a), one for reading
the value of a field (field-access) and the other when we write to a
field (field-write). Both rules first check that the operations can be
performed on a non-null location. The field-access rewrite rule
in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$ and
uses \figref{fig:symInit}, to get a new symbolic heap that is
initialized on the field $\cfgnt{f}$. The symbolic heap is further
modified to include a new stack reference pointing to the guarded value set
(possible values of the field) returned during the dereferencing; the
new stack reference is the return value from the operation.

### 2015-09-10 vmcai-2016-tex/bisimulation.tex
Corrected numerous typos throughout the paper.

In the lemma, $S$ is the universe of well-formed states, and the
set $S_A \subseteq S$ is states at a field access continuation having computed the base reference.
\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisimulation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

>>>>

In the following lemma, $S$ is the universe of well-formed states, and $S_{FA} \subseteq S$ is the set of states at a field access continuation having computed the base reference.
\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisimulation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

### 2015-09-10 vmcai-2016-tex/evaluation.tex
Corrected numerous typos throughout the paper.

%\subsection{Analysis}
Although the correctness of~\symtxt{} has been demonstrated,
it remains an open question whether it represents a practical alternative to the
case-splitting methods currently in use. It is possible 
that the benefit of decreasing the number of paths explored is
offset by the increased complexity of the underlying constraints problem.

@@

The results of the experiments are presented in Table~\ref{tab:results}. 
Each row reports the results for the specified $k$-bound 
for each artifact evaluated. The columns show the total
time in seconds, states explored, and paths generated for
each algorithm. The headings \gsetxt{}, L\#, and SH correspond
to the Generalized Symbolic Execution, Lazier\#, and \symtxt{}
algorithms, respectively. Note that we omit the results for
the Lazier algorithm because they are nearly identical to the Lazier\#
results for these artifacts. A table entry of  '-' indicates the analysis
exceeded the allotted time bound of 10 minutes.

Performance improvement ranges from $4.8x$ for
BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
for some $k$-bounds a number of experiments completed exploration
using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
$k$=8. The results demonstrate that for these common data structures,
the complexity of the constraints generated by~\symtxt{} is more 
than offset by the reduction in paths explored.

>>>>

%\subsection{Analysis}
Although the correctness of~\symtxt{} has been demonstrated,
it remains an open question whether it represents a practical alternative to the
case-splitting methods currently in use. It is possible 
that the benefit of decreasing the number of paths explored is
offset by the increased complexity of the resulting path condition.

@@

The results of the experiments are presented in Table~\ref{tab:results}. 
Each row reports the results for the specified $k$-bound 
for each artifact evaluated. The columns show the total
time in seconds, states explored, and paths generated for
each algorithm. The headings \gsetxt{}, L\#, and SH correspond
to the Generalized Symbolic Execution, Lazier\#, and \symtxt{}
algorithms, respectively. Note that we omit the results for
the Lazier algorithm because they are nearly identical to the Lazier\#
results for these artifacts. A table entry of  '-' indicates the analysis
exceeded the allotted time bound of 1 hour.

Performance improvement ranges from $4.8x$ for
BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
for some $k$-bounds a number of experiments complete exploration
using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# are
unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
$k$=8. The results demonstrate that for these common data structures,
the complexity of the constraints generated by~\symtxt{} is more 
than offset by the reduction in paths explored.

### 2015-09-10 vmcai-2016-tex/intro.tex
Corrected numerous typos throughout the paper.

In symbolic execution, the values of program variables are represented as constraints over the program’s inputs. During the course of an execution, a program variable may assume a number of possible values under a variety of different conditions. One way to represent this behavior is by pairing each possible value with the with the constraints under which it is assumed. A set of such value-constraint pairs, called a \emph{guarded value set}, represents the state of a program variable.

>>>>

In symbolic execution, the values of program variables are represented as constraints over the program's inputs. During the course of an execution, a program variable may assume a number of possible values under a variety of different conditions. One way to represent this behavior is by pairing each possible value with the constraints under which it is assumed. A set of such value-constraint pairs, called a \emph{guarded value set}\footnote{Guarded value sets are variously referred to in the literature as \emph{guarded location sets}, \emph{symbolic value sets}, or \emph{value summaries}. The term guarded value set is sometimes abbreviated in this text as~\emph{value set}.}, represents the state of a program variable.

### 2015-09-10 vmcai-2016-tex/lazy.tex
Corrected numerous typos throughout the paper.

The~\gsetxt{} initialization rules preserve several important properties of the symbolic heap. In the heap generated by~\gsetst{}, each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals}.
  Only input heap references appear in constraints to express potential aliasing.
  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations. Changes to $R$ are monotonically increasing, eliminating any need for constraint rewriting as the program state evolves.
A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

>>>>

The~\gsetxt{} initialization rules preserve several important properties of the symbolic heap. In the heap generated by~\gsetst{}, each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals}.
  Only input heap references appear in constraints to express potential aliasing.
  Auxiliary literals and stack references are used to define additional structure in the heap but only stack references can appear in environments, expressions, or continuations. Changes to $R$ are monotonically increasing, eliminating any need for constraint rewriting as the program state evolves.
A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

### 2015-09-10 vmcai-2016-tex/rw.tex
Corrected numerous typos throughout the paper.

\section{Related Work}
\label{sec:related}

\subsection{Program Analysis using Symbolic Heaps}
The symbolic heap methods in this work build upon a
number of prior program analysis techniques that use sets of guarded values to
represent program
state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. 
The method was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005,Yorsh:2008}, where value sets were used to 
represent aliasing-free tree-like heaps. The work in~\cite{Dillig:2011} relaxed the aliasing restrictions by using a pre-computed set of symbolic input heaps.

Recently, value sets have been adapted for use in symbolic execution, for the purposes of state merging ~\cite{Sen:2014,Torlak:2014} and invariant detection~\cite{Ferrara:2014}. While these methods demonstrate the utility of value sets in combination with symbolic execution, none of these techniques address dereferencing of symbolic input references. Since dereferencing is a fundamental problem treated in this paper, we believe these other works to be both orthogonal and complimentary to our own.

\subsection{Other Heap Representations in Symbolic Execution}
%Need to talk about GSE, DSE, SAGE, PEX
%GSE
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (\gsetxt{}) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion.

@@

\subsection{Formal Results on Symbolic Heaps}
The symbolic heap used by SAGE~\cite{Elkarablieh:2009} was shown to be sound and complete for programs with input-independent memory allocation. Our method is sound and complete for all states reached by symbolic execution.

>>>>

\section{Related Work}
\label{sec:related}
%
%\subsection{Program Analysis using Symbolic Heaps}
The symbolic heap methods in this work build upon a
number of prior program analysis techniques that use guarded value sets to
represent program
state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. 
The method was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005,Yorsh:2008}, where value sets were used to 
represent aliasing-free tree-like heaps. The work in~\cite{Dillig:2011} relaxed the aliasing restrictions by using a pre-computed set of symbolic input heaps.

Recently, value sets have been adapted for use in symbolic execution, for the purposes of state merging ~\cite{Sen:2014,Torlak:2014} and invariant detection~\cite{Ferrara:2014}. While these methods demonstrate the utility of value sets in combination with symbolic execution, none of these techniques address dereferencing of symbolic input references. Since dereferencing is a fundamental problem treated in this paper, we believe these other works to be both orthogonal and complimentary to our own.
%
%\subsection{Other Heap Representations in Symbolic Execution}
%Need to talk about GSE, DSE, SAGE, PEX
%GSE
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (\gsetxt{}) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion.

@@

%
%\subsection{Formal Results on Symbolic Heaps}
The symbolic heap used by SAGE~\cite{Elkarablieh:2009} was shown to be sound and complete for programs with input-independent memory allocation. Our method is sound and complete for all states reached by symbolic execution.

### 2015-09-10 vmcai-2016-tex/summary-heap.tex
Corrected numerous typos throughout the paper.

Symbolic execution semantics are is defined using
a small-step operational semantics similar to the one presented 
in~\cite{saints-MS}. The small-step semantics,
defined as a syntactic machine using a CESK architecture~\cite{Felleisen:1992},
are modified to perform symbolic execution on a symbolic heap. The
surface (input) syntax and machine (state) syntax are shown
in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness.

@@

Conceptually, the symbolic heap may be thought of as a bipartite graph. \figref{fig:exampleHeap} shows an example symbolic heap graph. References are 
represented by circles and locations are represented by squares. Arrows leaving
references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
arrows leaving the squares correspond to the $\cfgnt{R}$ function.

The machine state $\cfgnt{s}$ includes the program
registry $\mu$, the symbolic heap,
and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation.  The
more complex structures, such as the environment and heap, are defined
as singly linked lists of mappings that start with empty, \cfgnt{mt}. These lists are treated as
partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
$\cfgnt{k}$ indicates with $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
temporary computation, and keeps track of the next continuation. For
example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
expression for the object reference on which the field $\cfgnt{f}$ is
going to be accessed. Once the field access is complete, the machine
continues with $\cfgnt{k}$.

Execution begins with the initial machine state. The expression for the initial state constructs a new object of type
$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
object. The initial symbolic heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
$$
\begin{array}{l}
\lp\mu 
\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
\ \cfgnt{R}
\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
\end{array}
$$

@@

The rewrite relations for the portion of the language
semantics that are common to both generalized symbolic execution and
the symbolic heap algorithm may be found in \cite{Hillery:2015}. The relation $\rcom$ includes all of these
rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
the heap, and are largely concerned with argument evaluation in an
expected way. It is assumed that only type safe programs are input to
the machine so there is no type checking or error conditions. The
machine simply halts if no rewrite is enabled.

>>>>

Symbolic execution semantics are defined using
a small-step operational semantics similar to the one presented 
in~\cite{saints-MS}. The small-step semantics,
defined as a syntactic machine using a CESK architecture~\cite{Felleisen:1992},
are modified to perform symbolic execution on a symbolic heap. The
surface (input) syntax and machine (state) syntax are shown
in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness.

@@

Conceptually, the symbolic heap may be thought of as a bipartite graph. \figref{fig:exampleHeap} shows an example symbolic heap graph. References are 
represented by circles and locations are represented by squares. Arrows leaving
references correspond to the guarded value sets returned by the $\cfgnt{L}$ function, and 
arrows leaving the squares correspond to the $\cfgnt{R}$ function.

The machine state $\cfgnt{s}$ includes the program
registry $\mu$, the symbolic heap,
and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation.  The
more complex structures, such as the environment and heap, are defined
as singly linked lists of mappings that start with empty, \cfgnt{mt}. These lists are treated as
partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
$\cfgnt{k}$ indicates with the symbol $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
temporary computation, and keeps track of the next continuation. For
example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
expression for the object reference on which the field $\cfgnt{f}$ is
going to be accessed. Once the field access is complete, the machine
continues with $\cfgnt{k}$.

Execution begins with the initial machine state. The expression for the initial state constructs a new object of type
$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
object. The initial symbolic heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized
  ($\cfgnt{l}_\mathit{un}$),  with corresponding references 
  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
$$
\begin{array}{l}
\lp\mu 
\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
\ \cfgnt{R}
\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
\end{array}
$$

@@

The rewrite relations for the portion of the language
semantics that are common to both generalized symbolic execution and
the symbolic heap algorithm may be found in \cite{Hillery:2015}. The relation $\rcom$ includes all of these
rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
the heap, and are largely concerned with argument evaluation in an
expected way. It is assumed that only type safe programs are input to
the machine so there is no type checking. The
machine halts if no rewrite is enabled.
